R Notebook

### 2017-04-03 doc/RMD/MLG-distribution.Rmd
add section

Now that we have the adjacency matrix, we can use it to construct our graph:

```{r, fig.width = 7, fig.height = 7}
graph16loc <- make_graph_list(dat)
graph11loc <- make_graph_list(dat[loc = keeploci, mlg.reset = TRUE])

par(mfrow = c(3, 4))
plot_mlg_subgraph(graph16loc[-length(graph16loc)])

@@

par(mfrow = c(1, 1))
plot_mlg_graph(graph16loc$total, good_layout)
plot_mlg_graph(graph11loc$total, good_layout)
```

>>>>

## Graphs

With the fuctions above, we can create and plot the graphs

```{r, fig.width = 7, fig.height = 7}
# Creating the graphs
graph16loc <- make_graph_list(dat)
graph11loc <- make_graph_list(dat[loc = keeploci, mlg.reset = TRUE])

# Plotting the subgraphs
par(mfrow = c(3, 4))
plot_mlg_subgraph(graph16loc[-length(graph16loc)])

@@

# Plotting the full graphs
par(mfrow = c(1, 1))
plot_mlg_graph(graph16loc$total, good_layout)
plot_mlg_graph(graph11loc$total, good_layout)
```
